Polyglots: Crossing Origins by Crossing Formats

### 2013-06-27 rebuttal.txt

To reviewers:

We would like to thank the reviewers for the valuable feedback.

@@

The novelty of this paper, in relation to PDFs, lies not in showing how a PDF can be malicious, 
but rather to show how the flexibility of the format makes it ideal for hiding a malicious PDF 
in another format. In relation to Flash, it is not attempting to show that Flash is vulnerable, 
but rather to show how PDF can serve as a delivery mechanism for malicious Flash. Future work 
mentions scriptable media formats, e.g., Advanced Streaming Format (ASF), as another problem area.
However, space constraints prohibited us from further exploring these formats within the scope 
of this paper.

As to the generality of the work: In comparison to Barth et al., who only consider formats
that are combined with malicious HTML, we show that the issue extends far beyond HTML, and
that other formats can be abused in a web context, thereby making the results more
general.

Regarding more in-depth defenses, we will be happy to include in the paper a discussion of
most promising directions in this space. For example, note that when content is loaded in
a specific context, as it is in the case of the paper, the browser already has exact
knowledge as to what type it will interpret the requested content as. A natural defense
technique can be to send the expected type along with the request. The web server then
can compare the types and react accordingly. Further, It can be implemented in the web
server itself (as opposed to the web application), since the web server makes the final
decision on the supplied content-type. This can help mitigate both syntax injection and
content smuggling.

@@

Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
(since ca. 2008), but considered to be of little importance. Our reports may have influenced 
Adobe's decision to finally remove them, but it is not known to us to what extent.

As suggested, the visualization will be updated for a more professional appearance, 
and the listings moved to their appropriate positions. Finally, all typos have been corrected.

### 2013-06-28 rebuttal.txt

We would like to thank the reviewers for the valuable feedback.

Novelty:

The novelty of this paper, in relation to PDFs, lies not in showing how a PDF can be malicious, 
but rather to show how the flexibility of the format makes it ideal for hiding a malicious PDF 
in another format. In relation to Flash, it is not attempting to show that Flash is vulnerable, 
but rather to show how PDF can serve as a delivery mechanism for malicious Flash. Future work 
mentions scriptable media formats, e.g., Advanced Streaming Format (ASF), as another problem area.
However, space constraints prohibited us from further exploring these formats within the scope 
of this paper.

Generality:

As proposed, we plan to make the claims of generality more precise, with our high-level
presentation of polyglots and their abuse possibilities as general, and the focus on new
PDF-based attacks as particular. Similarly, we agree it is a good idea to clarify the
general vs. particular aspects of mitigation.

In comparison to Barth et al., who only consider formats that are combined with malicious
HTML, we show that the issue extends far beyond HTML, and that other formats can be abused
in a web context, thereby making the results more general.

Advanced mitigation:

Regarding more advanced defenses, we will be happy to include in the paper a discussion of
most promising directions in this space. For example, note that when content is loaded in
a specific context, as it is in the case of the paper, the browser already has exact
knowledge as to what type it will interpret the requested content as. A natural defense
technique can be to send the expected type along with the request. The web server then
can compare the types and react accordingly. Further, It can be implemented in the web
server itself (as opposed to the web application), since the web server makes the final
decision on the supplied content-type. This can help mitigate both syntax injection and
content smuggling.

@@

Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
(since ca. 2008), but considered to be of little importance. Our reports may have influenced 
Adobe's decision to finally remove them, but it is not known to us to what extent.

As suggested, we plan make the treatment of the related work more coherent.

### 2013-06-28 rebuttal.txt

To reviewers:

We would like to thank the reviewers for the valuable feedback.

Our paper builds on the work of Barth et al. who show how malicious HTML hidden in other file 
formats can trick the browser's content-sniffing algorithm into rendering the file as HTML. Taking 
into account previous instances of similar attacks, we show that the issue extends beyond content-
sniffing, and generalize an attack pattern, polyglot attacks, where formats are cross-bred to hide 
a malicious file. The novelty of this paper lies in (1) generalizing polyglot attacks, and (2) 
showing practical that can be abused in a web context.

In this paper we show that a PDF document can embed new class 
of 
attacks,  where polyglots...
As to the generality of the work:

Apart from generalizing the concept of polyglot attacks, our paper shows how the flexibility of 
the PDF format makes it ideal for hiding a malicious PDF in another format.

 in relation to PDFs, lies in showing how the flexibility of the format 
makes it ideal for hiding a malicious PDF 
in another format. In relation to Flash, it is not attempting to show that Flash is vulnerable, 
but rather to show how PDF can serve as a delivery mechanism for malicious Flash. Future work 
mentions scriptable media formats, e.g., Advanced Streaming Format (ASF), as another problem area.
However, space constraints prohibited us from further exploring these formats within the scope 
of this paper.

Regarding more advanced defenses, we will be happy to include in the paper a discussion of
most promising directions in this space. For example, note that when content is loaded in
a specific context, as it is in the case of the paper, the browser already has exact
knowledge as to what type it will interpret the requested content as. A natural defense
technique can be to send the expected type along with the request. The web server then
can compare the types and react accordingly. Further, It can be implemented in the web
server itself (as opposed to the web application), since the web server makes the final
decision on the supplied content-type. This can help mitigate both syntax injection and
content smuggling.

### 2013-06-29 rebuttal.txt

We would like to thank the reviewers for their valuable feedback.

Our paper builds on the work of Barth et al., who show how a carefully crafted file of a benign 
format can manipulate the browser's content-sniffing algorithm into rendering the file as 
malicious HTML. Taking into account previous instances of similar attacks, we show that the issue 
extends beyond content-sniffing, and how other formats can be abused in a web context, thereby 
generalizing the polyglot attack pattern.

@@

Our paper builds on the work of Barth et al., who show how a carefully crafted file of a benign 
format can manipulate the browser's content-sniffing algorithm into rendering the file as 
malicious HTML. Taking into account previous instances of similar attacks, we show that the issue 
extends beyond content-sniffing, and how other formats can be abused in a web context, thereby 
generalizing the polyglot attack pattern.

As proposed, we plan to make the claims of generality more precise, with our high-level
presentation of polyglots and their abuse possibilities as general, and the focus on new
PDF-based attacks as particular. Similarly, we agree it is a good idea to clarify the
general vs. particular aspects of mitigation.

Novelty:

The novelty of this paper is twofold; generalizing polyglot attacks, and showing a practical 
example of a vulnerable format. We show how the flexibility of the PDF format makes it ideal for 
hiding a malicious PDF document in a benign format. We also discuss PDF as a delivery mechanism 
for an embedded malicious Flash. The resulting polyglot has the flexibility of PDF and the 
capabilities of PDF and Flash combined.

As for other vulnerable formats, future work mentions scriptable media formats, e.g., Advanced 
Streaming Format (ASF), as another problem area. However, space constraints prohibits us from 
further exploring these formats within the scope of this paper.

@@

Advanced mitigation:

Regarding more advanced defenses, we will be happy to include in the paper a discussion of
most promising directions in this space. For example, note that when content is loaded in
a specific context, as it is in the case of the paper, the browser already has exact
knowledge as to what type it will interpret the requested content as. A natural defense
technique can be to send the expected type along with the request. The web server then
can compare the types and react accordingly. Further, it can be implemented in the web
server itself (as opposed to the web application), since the web server makes the final
decision on the supplied content-type. This can help mitigate both syntax injection and
content smuggling.

Evaluation of mobile browsers would indeed make an interesting addition, and certainly one we 
would like to delve further into.

Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
(since ca. 2005), but considered to be of low priority. Our reports may have influenced Adobe's 
decision to finally remove them, but it is not known to us to what extent.

As suggested, we plan to make the treatment of the related work more coherent. Also, as suggested, 
the visualization will be updated for a more professional appearance, and the listings moved to 
their appropriate positions. Finally, all typos have been corrected, and we are working on 
clarifying the complex sections, starting from your suggestions.

### 2013-06-29 rebuttal.txt

We would like to thank the reviewers for the valuable feedback.

@@

Generality:

Barth et al. show how a carefully crafted file of a benign format can manipulate the
browser's content-sniffing algorithm into rendering the file as malicious HTML. With this
and other similar attacks as a starting point, we show that the issue extends beyond
content sniffing and demonstrate how other formats can be abused in a web context, thereby
generalizing polyglot-based attacks.

Following the suggestion, we plan to make the claims of generality more precise, with our
high-level presentation of polyglots and their abuse possibilities as general, and the
focus on new PDF-based attacks as particular. Similarly, we agree it is a good idea to
clarify the general vs. particular aspects of mitigation.

@@

Novelty:

The novelty of this paper is twofold: generalizing polyglot attacks and showing a practical 
example of a vulnerable format. We show how the flexibility of the PDF format accommodates 
hiding a malicious PDF document in a benign format. We also discuss PDF as a delivery mechanism 
for an embedded malicious Flash. The resulting polyglot has the flexibility of PDF and the 
capabilities of PDF and Flash combined.

@@

As for other vulnerable formats, future work mentions scriptable media formats, e.g., Advanced 
Streaming Format (ASF), as another problem area. However, space constraints prohibits us from 
further exploring these formats within the scope of this paper.

Advanced mitigation:

Regarding more advanced defenses, we will be happy to include in the paper a discussion of
most promising directions in this space. For example, note that when content is loaded in
a specific context, as it is in the case of the paper, the browser already has exact
knowledge as to what type it will interpret the requested content as. A natural defense
technique can be to send the expected type along with the request. The web server then
can compare the types and react accordingly. Further, it can be implemented in the web
server itself (as opposed to the web application), since the web server makes the final
decision on the supplied content-type. This can help mitigate both syntax injection and
content smuggling.

Evaluation of mobile browsers would indeed make an interesting addition, and certainly one we 
would like to delve into further.

@@

Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
(since ca. 2005), but considered to be of low priority. Our reports may have influenced Adobe's 
decision to finally remove them, but it is not known to us to what extent.

As suggested, we plan to make the treatment of the related work more coherent. Also, we
are happy to follow the suggestion to update the visualization with a more professional
appearance and to move the listings to their appropriate positions.

### 2013-06-29 rebuttal.txt

Barth et al. show how a carefully crafted file of a benign format can manipulate the
browser's content-sniffing algorithm into rendering the file as malicious HTML. With this
and other similar attacks as a starting point, we show that the issue extends beyond
content sniffing and demonstrate how other formats can be abused in a web context, thereby
generalizing polyglot-based attacks.

Following the suggestion, we plan to make the claims of generality more precise, with our
high-level presentation of polyglots and their abuse possibilities as general, and the
focus on new PDF-based attacks as particular. Similarly, we agree it is a good idea to
clarify the general vs. particular aspects of mitigation.

Novelty:

The novelty of this paper is twofold: generalizing polyglot attacks and showing a practical 
example of a vulnerable format. As mentioned, malicious PDFs or Flash is no surprise. However, we 
show how the flexibility of the PDF format accommodates hiding such	a malicious PDF document in a 
benign format. We also discuss PDF as a delivery mechanism for an embedded malicious Flash. The 
result has the flexibility of PDF to be crossbred with other formats, and the capabilities of PDF 
and Flash combined.

@@

As for other vulnerable formats, future work mentions scriptable media formats, e.g., Advanced 
Streaming Format (ASF), as another problem area. However, space constraints prohibits us from 
further exploring these formats within the scope of this paper.

Advanced mitigation:

Regarding more advanced defenses, we will be happy to include in the paper a discussion of
most promising directions in this space. For example, note that when content is loaded in
a specific context, as it is in the case of the paper, the browser already has exact
knowledge as to what type it will interpret the requested content as. A natural defense
technique can be to send the expected type along with the request. The web server then
can compare the types and react accordingly. Further, it can be implemented in the web
server itself (as opposed to the web application), since the web server makes the final
decision on the supplied content-type. This co-operation between client and server can help 
mitigate both syntax injection and content smuggling. A proof-of-concept implementation would 
require minimal adjustments on both client- and server-side and an evaluation could be done easily.

The evaluation may well be too focused on PDF-based polyglot attacks, and would benefit from more 
general tests. Evaluation of mobile browsers would indeed make an interesting addition, and 
certainly one we would like to delve into further.

@@

### Jonas ###
# In relation to Flash, it is not attempting to show that Flash is vulnerable, but rather to show
# how PDF can serve as a delivery mechanism for malicious Flash.
#############

It would have been interesting to delve into more surprising formats. The paper from Barth et al. 
looks at malicious PostScript, and PDF, while not being quite as bad, has certainly suffered from 
its share of problems.

### Jonas ###
# Future work mentions scriptable media formats, such as Windows Media Format, as another problem area.
# However, space constraints prohibited us from further exploring these formats within the scope of this paper.
#############

The evaluation for this paper felt somewhat pro forma. I would have rather seen a more extensive 
set of tests against the individual browsers,

### Jonas ###
# THe evaluation is indeed focused on PDF-based polyglots, thereby not making it general 
#############

and perhaps to have considered mobile web browsers 
as well.

@@

### Jonas ###
# Mobile browsers would indeed make an interesting addition.
#############

Where I think the paper was particularly lacking was on the mitigation side. For a venue such as 
this, I would have liked to have seen an implementation of one of the mitigation solutions and a 
full evaluation of security and performance. This could be done either on the browser or server 
side. Without that, this paper has more of an informational feel to it.

### Jonas ###
# This mitigation technique 
# Implementing this mitigation technique would require adjustments on both
#
#############

### 2013-06-30 rebuttal.txt

Thank you to the reviewers for the valuable feedback.

Generality:

Barth et al. show how a carefully crafted file of a benign format can manipulate the
browser's content-sniffing algorithm into rendering the file as malicious HTML. With this
and similar attacks as a starting point, we show that the issue extends beyond content
sniffing and demonstrate how other formats can be abused in a web context, thereby
generalizing polyglot-based attacks.

@@

The novelty of this paper is twofold: generalizing polyglot attacks and showing a
practical example of a vulnerable format. As mentioned, malicious PDFs or Flash is no
surprise. However, we show how the flexibility of the PDF format accommodates hiding such
a malicious PDF document in a benign format. We also discuss PDF as a delivery mechanism
for an embedded malicious Flash. The result has the flexibility of PDF to be crossbred
with other formats, and the capabilities of PDF and Flash combined.

As for other vulnerable formats, future work mentions scriptable media formats, e.g.,
Advanced Streaming Format (ASF), as another problem area. However, space constraints
prohibits us from further exploring these formats within the scope of this paper.

Advanced mitigation:

We are convinced the mitigation techniques we suggest are both most needed and
realistically deployable. Regarding more advanced defenses, we will be happy to include in
the paper a discussion of most promising directions. For example, note that when content
is loaded in a specific context, as it is in the case of the paper, the browser already
has exact knowledge as to what type it will interpret the requested content as. A natural
defense technique can be to send the expected type along with the request. The web server
then can compare the types and react accordingly. Further, it can be implemented in the
web server itself (as opposed to the web application), since the web server makes the
final decision on the supplied content-type. This cooperation between client and server
can help mitigate both syntax injection and content smuggling.

Evaluation of mobile browsers would indeed make an interesting addition, and certainly one
we would like to delve into further.

@@

Concerning XML External Entities (XXE) in Adobe Reader, the problem of XXE was previously known 
(since ca. 2005), but considered to be of low priority. Our reports may have influenced Adobe's 
decision to finally remove them, but it is not known to us to what extent.

We plan to make the treatment of the related work more coherent. Also, we are happy to
follow the suggestion to update the visualization with a more professional appearance, to
move the listings to their appropriate positions and generally clarify the exposition
where appropriate.

### 2013-08-08 main.tex
Updated the rebuttal and fixed typo in the article.
Literally just removed a comma.
no message

XSS attacks are relatively well understood by researchers and
developers~\cite{XSSED}. Known defense include various
flavors of \emph{sanitization} on server side and the
\emph{content security policy}~\cite{CSP1.0} (CSP) on client side. Sanitization
is often performed by the server to filter possibly malicious input data
before it is used in the generated web pages. Content security policy puts
requirement on the structure of the document and the origins of the
scripts that are included by web pages.

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded in the attackers web site using a plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested, thus allowing the polyglot to communicate with the vulnerable 
origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\subsubsection{Readers}
\label{sec:readers}
Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
due to its standing as the most commonly used reader. To give a comparison, the 
Google Chrome built-in PDF reader, was selected as it is the default reader to 
user of the browser.

>>>>

XSS attacks are relatively well understood by researchers and
developers~\cite{XSSED}. Known defenses include various
flavors of \emph{sanitization} on server side and the
\emph{content security policy}~\cite{CSP1.0} (CSP) on client side. Sanitization
is often performed by the server to filter possibly malicious input data
before it is used in the generated web pages. Content security policy puts
requirement on the structure of the document and the origins of the
scripts that are included by web pages.

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded in the attacker's web site using a plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which the content was requested, thus allowing the polyglot to communicate with the vulnerable 
origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\subsubsection{Readers}
\label{sec:readers}
Section~\ref{sec:vuln} focuses on the Adobe PDF Reader as the attack surface, 
due to its standing as the most commonly used reader. To give a comparison, the 
Google Chrome built-in PDF reader was selected as it is the default reader to 
users of the browser.
